Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-26 article.tex
bookmark

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(\cref{eq:beer-lambert,eq:betair,eq:tautotal}) the radiant power
contributed by the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  \exp\{-\tau_c(k)\}
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bm p}_c= L^{\rm TOA}
  [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
  \odot \exp\{-\vect{\tau}_c\}
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone includes some voxels, intersects with some other
voxels, and oblivious to all the rest~(\cref{fig:projection}b).
% \begin{figure}
%   \centering
%   \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
%   \caption{\small [a] Irradiance of voxel $k$ is attenuated by
%   voxels above it on a SR. The scattered radiance from voxel $k$ is
%   then attenuated by voxels below it on a LOS to camera $c$.  [b] An
%   image pixel captures light emanating in a cone in space. Voxels
%   that fully or partially fall in this cone are sensed by the
%   pixel.}
%   \label{fig:projection}
% \end{figure}
Thus light power captured at a pixel is a weighted sum of the power
$p_c(k)$ from all voxels.  This linear sum is formulated by a matrix
operation over ${\bm p}_c$. The measured image is column-stacked to a
vector $N_{\rm pix}$ long. It is given by
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;.
  \label{eq:IcP}
\end{equation}

@@

To simplify the case in study, let us assume there is only a single
type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\bm n}$ is variable. Then,
\cref{eq:bigIc} degenerates to
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
  \exp\{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol} {\bm D}_c
  {\bm n})\}\odot [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
    aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
    scatter}_c) \odot{\bm n} ] \Big\} .
  \label{eq:bigIA}
\end{align}

>>>>

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(\cref{eq:beer-lambert,eq:betair,eq:tautotal}) the radiant power
contributed by the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  \exp[-\tau_c(k)]
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bm p}_c= L^{\rm TOA}
  [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
  \odot \exp(-\vect{\tau}_c)
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone contains or intersects some voxels, while being oblivious to all the rest~(\cref{fig:projection}b).
% \begin{figure}
%   \centering
%   \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
%   \caption{\small [a] Irradiance of voxel $k$ is attenuated by
%   voxels above it on a SR. The scattered radiance from voxel $k$ is
%   then attenuated by voxels below it on a LOS to camera $c$.  [b] An
%   image pixel captures light emanating in a cone in space. Voxels
%   that fully or partially fall in this cone are sensed by the
%   pixel.}
%   \label{fig:projection}
% \end{figure}
Overall, light power captured at a pixel is a weighted sum of the power
$p_c(k)$ from all voxels.  This sum is formulated by a matrix
operation over ${\bm p}_c$:
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;,
  \label{eq:IcP}
\end{equation}
where ${\bm i}_c$ is the image, column-stacked to a
vector $N_{\rm pix}$ long.

@@

To simplify the case in study, we focus on situations in which there is only a single
type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\bm n}$ is variable. Then,
\cref{eq:bigIc} degenerates to
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
  \exp\{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol} {\bm D}_c
  {\bm n})\}\odot [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
    aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
    scatter}_c) \odot{\bm n} ] \Big\} .
  \label{eq:bigIA}
\end{align}
